---
title: "Homework 1"
author: "Anusorn Thanataveerat"
date: '2018-09-13'
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r sample_chunk, echo = TRUE}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp), 3)`.
`this is code mean(samp)`


Learning assessment: Write a named code chunk that creates a variable containing a sample of size 500 from a random normal variable, computes the absolute value of each element, and produces a histogram of the result. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about  echo = FALSE?

```{r assessment2, echo = TRUE}
unif <- rnorm(500)
unif_abs <- abs(unif)
hist(unif_abs)
```


```{r plot_histogram, echo = TRUE}
# ggplot(unif_abs,)
library(tidyverse)
qplot(unif_abs, geom="histogram")

```


```{r learning_assessment_1}
la_df = tibble(
  norm_samp = rnorm(500),
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()
```

The median of the variable containing absolute values is 
`r round(median(la_df$abs_norm_samp), digits = 2)`.




